Introducing Distributed Dynamic Data-intensive (D3) Science: Understanding Applications and Infrastructure

### 2015-09-12 3dpas_intro.tex
changing order of affiliations

\author{Shantenu Jha\affil{1}\corrauth\, Daniel S. Katz\affil{4,5},
  Andre~Luckow\affil{1}, Omer Rana\affil{6}, Yogesh Simmhan\affil{7}, Neil Chue
  Hong\affil{2}, Simon Dobson\affil{3}}

\address{\affilnum{1}Rutgers University\break
\affilnum{2}University of Edinburgh\break
\affilnum{3}University of St.~Andrews\break
\affilnum{4}University of Chicago\break
\affilnum{5}Argonne National Laboratory\break
\affilnum{6}Cardiff University\break
\affilnum{7}Indian Institute of Science\break
}

>>>>

\author{Shantenu Jha\affil{1}\corrauth\, Daniel S. Katz\affil{2},
  Andre~Luckow\affil{1}, Omer Rana\affil{3}, Yogesh Simmhan\affil{4}, Neil Chue
  Hong\affil{5}, Simon Dobson\affil{6}}

\address{\affilnum{1}Rutgers University\break
\affilnum{2}University of Chicago \& Argonne National Laboratory\break
\affilnum{3}Cardiff University\break
\affilnum{4}Indian Institute of Science\break
\affilnum{5}University of Edinburgh\break
\affilnum{6}University of St.~Andrews\break
}
